### 2022-09-21 LaTeX/MSGARCH.tex
Adds some latex and scenario graphs

% MAKE subsubsubsection possible
\usepackage{titlesec}

@@

\subsubsection{GARCH}
GARCH (General Autoregressive Conditional Heteroskedasticity) has been popular in order to forecast the volatility of indices. It tries to explain the observation that the volatility of an asset tends to cluster, i.e. periods with high volatility are followed by periods with high volatility.
however the model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).
The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
$$y_{l} \mid\left(s_{l}=k, \mathcal{I}_{l-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
$\mathcal{D}$ being some zero-mean distribution, the variance h and shape parameters $\xi$. For short time-periods the zero-mean specification is justified most of the time.  $s_t$ is the state at time t is modeled by a Markov chain.\\

A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$. Similar to an ARMA model which tries specify the conditional mean, the GARCH model tries to specify the conditional variance. The lagged squared return term can be interpreted as a proxy for the realized variance in the last observation period. 
Long periods of high variance can be modeled by increasing the intercept $\beta$.\\

Many extensions of the GARCH model exist, like (todo). The TGARCH e.g. tries to incorporate the observation that variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
$$h_{k, t}^{1 / 2} \equiv \alpha_{0, k}+\left(\alpha_{1, k} \mathbb{I}\left\{y_{t-1} \geq 0\right\}-\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}+\beta_{k} h_{k, t-1}^{1 / 2}$$

@@

>>>>

% HINZUGEFÜGT VON ADRIAN
% MAKE subsubsubsection possible
\usepackage{titlesec}
\usepackage{cleveref}
\usepackage{acronym}

\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}

@@

\subsubsection{Heavy-tailed Distributions}
Many different distributions have been suggested for modeling asset returns, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions.
In this paper we will use the \ac{GED}, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered.
$$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$

\subsubsection{GARCH}
\label{sss:GARCH}
The \ac{GARCH} model has been popular in order to forecast the volatility of indices. It was introduced XXXX by \cite{} and is an extension of the ARCH model, which was introduced Engle \cite{}. It models the error by using a \ac{ARMA} model.
It tries to explain the observation that the volatility of financial assets tends to be heteroskedastic and cluster, i.e. periods with high volatility are followed by periods with high volatility.

The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
Denote $y_t$ the log-returns in time period $t$, i.e. $log(p_t-p_{t-1})$ if $p_t$ is the asset price at time t.

$$y_{t} \mid\left(s_{t}=k, \mathcal{I}_{t-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$

$\mathcal{D}$ being some zero-mean distribution, the conditional variance$h_{k,t}$ in state $k$ at time $t$ and shape parameters $\xi$. For short time-periods the zero-mean specification is justified most of the time.  $s_t$ is the state at time t is modeled by a Markov chain.\\

A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$ models the conditional variance process. $h_{k,t}$ is the conditional variance. Similar to an \ac{ARMA} model which tries specify the conditional mean, the \ac{GARCH} model tries to specify the conditional variance. The lagged squared return term can be interpreted as a proxy for the realized variance in the last observation period. 
In this model long periods of high variance can be modeled by increasing the intercept $\beta$.\\

Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns. One example is the GJR model by \cite{}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$

However the GARCH model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).

@@

For the GARCH as well as for the MSGARCH models we will use a \ac{SGED} to describe the distribution of the log-returns.
Also, GJR-GARCH is used for both of the models, see \cref{sss:GARCH}.
